Multi-Agent Path Finding with Matching using Increasing Cost Tree Search

### 2021-06-07 docs/paper.tex
Added claim about exhaustive method with sorting

	In practice, joint MDDs are not explicitly constructed but instead a depth-first search is used to search joint MDDs. This has the benefit of finding a path to the bottom of the joint MDD fast if one exists, while not constructing more of the joint MDD (which can get rather large) than is necessary for finding a solution.
	\subsubsection{ICTS with Independence Detection}
	Like many other MAPF algorithms, ICTS can be embedded in the Independence Detection (ID) framework introduced in \cite{standley2010}. ID starts by assuming each agent is a group that can be assigned an optimal path independent of other groups. If group paths do conflict, they become one group that is planned together using a MAPF algorithm, in this case ICTS, until no conflicts between groups occur. The goal of ID is to minimize $k'$, the size of the largest group that has to be planned. Optionally, a conflict avoidance table (CAT) can be maintained for use during planning of groups. This records the paths planned by other groups and can facilitate tie-breaking in search that minimizes the number of conflicts; the CAT is omitted from listing \ref{id-algo} for brevity but was implemented and used in experiments.
	\begin{algorithm}
	\begin{algorithmic}[1]
		\State \text{Assign each agent to a singleton group}
		\State \text{plan a path for each group}
		\Repeat
			\State \text{simulate execution of all paths until a conflict occurs}
			\State \text{merge two conflicting groups into a single group}
			\State \text{cooperatively plan new group}
		\Until{\text{no conflicts occur}}
		\State $solution\gets\text{paths of all groups combined}$
		\State \textbf{return solution}
	\end{algorithmic}
	\caption{Simple Independence Detection by Standley} 
	\label{id-algo}
	\end{algorithm}

@@

	The full ICT-search algorithm including a pruning step is described by pseudocode listing \ref{icts-algo}. It is reproduced from \cite{sharon2011} for completeness.
	\begin{algorithm}
		\begin{algorithmic}[1]
			\Procedure{ICT-search}{MAPF instance}
			\State \text{Construct ICT root}
			\ForAll{\text{ICT nodes }$(c_1,\ldots,c_k)$\text{ in breadth-first order }} 
				\ForAll{\text{agents} $a_i$} 
					\text{Construct} $MDD_i^{c_i}$
				\EndFor
				\ForAll{$j$-\text{agent combinations} $(i_1,\ldots,i_j)$} 
				\State \text{Run node-pruning procedure with MDDs }$MDD_{i_1}^{c_{i_1}},\ldots,MDD_{i_j}^{c_{i_j}}$
				\If{\text{no solution was found for a combination in pruning}}
					\State \textbf{Break}\text{ and continue with next ICT node}
				\EndIf
				\EndFor
				\State \text{Search }$k$\text{-agent MDD space}
				\If{\text{solution was found}}
				\State \textbf{return solution}
				\EndIf
			\EndFor

@@

%
	\section{Solving MAPF with Matching using ICTS} % Your contribution
	\label{section:icts-matching}
	Taking ICTS for MAPF as starting point, two methods to use ICTS for MAPFM were identified. The first method relies on the well-known reduction from MAPFM to repeated MAPF: any optimal solution to MAPFM corresponds to a matching of agents to goals, so by exhaustively enumerating all matchings and solving these as MAPF instances, an optimal solution to the MAPFM instance can be found. In the second method, the increasing cost trees search itself is modified to allow an agent $a_j^i$ to be matched to any $g_k^i$. For each method, some properties and method-specific optimizations and variations will be discussed. Afterwards, some more general considerations will be discussed.
	\subsection{Exhaustive ICTS}
	For $K$ teams $t_1,\ldots,t_K$ of size $t_i$, there are in total $M = \prod_{i} k_i!$ matchings from team agents to team goals. Let $C_1$ through $C_M$ denote the optimal SIC costs of each MAPF instance corresponding to the instance, with $C_m = \infty$ for unfeasible $m$. Let $\Delta_m$ be similarly defined and represent the difference between $C_m$ and the root cost of $m$.

	In order to find the optimal solution, $m$ with lowest $C_m$ has to be found, which requires all $M$ to be solved or marked as unfeasible, meaning that $\mathcal{O}(M)$ MAPF instances have to be solved. However, once the first solution is found with cost $C_m$, this can be used in the next search as an (exclusive) upper-bound for the SIC of nodes. Formally, let $B = \infty$ represent the initial SIC bound of the ICT search. After solving $C_m$, let $B_{new} = \min(B,C_m)$. By successively contracting this upper-bound on solution SIC, as more matchings are solved, the effort needed to solve the remaining matchings can be expected to be reduced significantly.

	 the effort needed to solve the remaining matchings can greatly be reduced.

	 and effectively depth-limiting the ICT traversal.

>>>>

	In practice, joint MDDs are not explicitly constructed but instead a depth-first search is used to search joint MDDs. This has the benefit of finding a path to the bottom of the joint MDD fast if one exists, while not constructing more of the joint MDD (which can get rather large) than is necessary for finding a solution.
	\subsubsection{ICTS with Independence Detection}
	Like many other MAPF algorithms, ICTS can be embedded in the Independence Detection (ID) framework introduced by Standley in \cite{standley2010}. ID starts by assuming each agent is a group that can be assigned an optimal path independent of other groups. If group paths do conflict, they become one group that is planned together using a MAPF algorithm, in this case ICTS, until no conflicts between groups occur. The goal of ID is to minimize $k'$, the size of the largest group that has to be planned. Optionally, a conflict avoidance table (CAT) can be maintained for use during planning of groups. This records the paths planned by other groups and can facilitate tie-breaking in search that minimizes the number of conflicts; the CAT is omitted from Algorithm \ref{id-algo} for brevity but was implemented and used in experiments.
	\begin{algorithm}
	\begin{algorithmic}[1]
		\State \text{Assign each agent to a singleton group}
		\State \text{plan a path for each group}
		\Repeat
			\State \text{simulate execution of all paths until a conflict occurs}
			\State \text{merge two conflicting groups into a single group}
			\State \text{cooperatively plan new group}
		\Until{\text{no conflicts occur}}
		\State $solution\gets\text{paths of all groups combined}$
		\State \textbf{return solution}
	\end{algorithmic}
	\caption{Simple Independence Detection by Standley} 
	\label{id-algo}
	\end{algorithm}

@@

	The full ICT-search algorithm including a pruning step is described by Algorithm \ref{icts-algo}. It is reproduced from \cite{sharon2011} for completeness. As noted before, this procedure could be used for planning groups in Algorithm \ref{id-algo}. 
	\begin{algorithm}
		\begin{algorithmic}[1]
			\Procedure{ICT-search}{MAPF instance}
			\State \text{Construct ICT root}
			\ForAll{\text{ICT nodes }$(c_1,\ldots,c_k)$\text{ in breadth-first order }} 
				\ForAll{\text{agents} $a_i$} 
					\text{Construct} $MDD_i^{c_i}$
				\EndFor
				\ForAll{$j$-\text{agent combinations} $(i_1,\ldots,i_j)$} 
				\State \text{Run node-pruning procedure with MDDs }$MDD_{i_1}^{c_{i_1}},\ldots,MDD_{i_j}^{c_{i_j}}$
				\If{\text{no solution was found for a combination in pruning}}
					\State \textbf{Break}\text{ and continue with next ICT node}
				\EndIf
				\EndFor
				\State \text{Search }$k$\text{-agent MDD space}
				\If{\text{solution was found}}
				\State \textbf{return solution}
				\EndIf
			\EndFor

@@

%
	\section{Solving MAPF with Matching using ICTS} % Your contribution
	\label{section:icts-matching}
	Taking ICTS for MAPF as starting point, two methods to use ICTS for MAPFM were identified. The first method relies on the well-known reduction from MAPFM to repeated MAPF: any optimal solution to MAPFM corresponds to a matching of agents to goals, so by exhaustively enumerating all matchings and solving these as MAPF instances, an optimal solution to the MAPFM instance can be found. In the second method, the increasing cost trees search itself is modified to allow an agent $a_j^i$ to be matched to any $g_k^i$. For each method, some properties and method-specific optimizations and variations will be discussed. Afterwards, some more general considerations will be discussed.
	\subsection{Exhaustive ICTS}
	For $K$ teams $t_1,\ldots,t_K$ of size $t_i$, there are in total $M = \prod_{i} k_i!$ matchings from team agents to team goals. Let $C_1$ through $C_M$ denote the optimal SIC costs of each MAPF instance corresponding to the instance, with $C_m = \infty$ for unfeasible $m$. Let $\Delta_m$ be similarly defined and represent the difference between $C_m$ and the root cost of $m$. In order to find the optimal solution, $m$ with lowest $C_m$ has to be found, which requires all $M$ to be solved or marked as unfeasible, meaning that $\mathcal{O}(M)$ MAPF instances have to be solved.

	However, once the first solution is found with cost $C_m$, this can be used in the next search as an (exclusive) upper-bound $B$ for the SIC of nodes. Formally, let $B = \infty$ represent the initial SIC bound of the ICT search. After solving each $C_m$, let $B_{m+1} = \min(B_m,C_m)$. By successively updating this $B$ in this manner, as more matchings are solved, the effort needed to solve the remaining matchings can be expected to be reduced significantly.

	As a further improvement of this method, the order in which matchings are enumerated and solved could be changed. In particular, by sorting the matchings in increasing order of root SIC, it can be seen that $\Delta'_{m + 1}$, the distance from $B_{m+1}$ or the solution to matching $m + 1$ (whichever was reached first) and the root SIC, will always be less or equal to the $\Delta'_m$ [TODO: proof]. Although this is itself a promising property, in order to make use of it, all roots have to be computed and all $M$ corresponding SIC values have to be sorted which is a $\mathcal{O}(M\log M)$ procedure.
